Self Referencing Sequences

### 2014-10-26 draft.tex
added def and notations section

\section{Definitions and Notations}
In this section we introduce

@@

\begin{theorem} If $1<a<b$ then the self-referencing sequence beginning with $a$ generated over $\{1, a, b\}$ and the self-referencing sequence beginning with $c_2$ generated over $\{1, a, b\}$ are independent.
\end{theorem}
\begin{proof}
We proceed by contradiction. If the two sequences are not independent then they must differ by some minimal prefix of length $n$. If we let $a_i$ be the sequence beginning with $a$ and $b_i$ be the sequence beginning with $b$ the
\begin{equation*}
a_{n+k} = b_{k}.
\end{equation*}
We know that the first $b$ terms of the sequence which begins with a $b$ are $b$'s. Because $b>a>1$ no block can be longer then $b$. Thus the terms immediately preceding and following this block in the sequence $a_i$ must not be $b$'s. Because of this the first block of $b_i$ is the $m+1$th block of $a_i$, where $m$ is some positive integer. Since the value of the sequence at position $k$ is also the length of the $k$th block this means that $a_{m+1}=b_1$. In fact the $k$th block of $b_i$ is the $(m+k)$th block of $a_i$ and so 
\begin{equation*}
a_{m+k} = b_k
\end{equation*}

@@

We note that based on a previous step the two sequences differ by a prefix starting at $m$. Since $m<n$ we have produced a prefix which starts before $n$ which is a contradiction. Therefore the two sequences are independent. 
\end{proof}
\end{document}

>>>>

\section{Definitions and Notations}

\emph{Written by Perry Kleinhenz, edited by Fermi Ma and Erik Waingarten}

In this section, we introduce the notation we will use for the remainder of this paper. Consider the sequence
\begin{align*}
1,2,2,1,1,2,1,2,2,1,2,2,1,1,2,1,1,2,2,1,2,1,1,...
\end{align*}
If we break the sequence up into contiguous blocks, where a block is a stretch of the sequence where only one number is used, we find that the block lengths of the sequence reproduce the original sequence. The first block length is 1, the second block length is 2, the third block length is 3, and so on.

We say that this sequence is \emph{generated} by the set of numbers used in the sequence, so this sequence is generated by $\{1,2\}$. We call this set the \emph{generating set}. Note that here, it is unambiguous which number to use ``next". After a block of 1's, the only choice for the next block is the number 2. However, if a sequence had the generating set $\{1,2,3\}$, for example, a block of 1's could be followed by either a block of 2's or a block of 3's. Thus, we will assume that a \emph{rule} is given whenever a sequence is generated by more than 2 numbers. In particular, the rule will be to use the next number (in cyclic order) in the generating set. Note here that the set is not a set in the formal sense, as the order does not matter. However, we avoid naming it a ``sequence" to avoid possible confusion with its corresponding self-referencing sequence.

With this rule, a the self-referencing sequence generated by $\{1,2,3\}$ has blocks of 1's followed by blocks of 2's followed by blocks of 3's, followed by blocks of 1's, and so on. Thus, the sequence is

@@

\begin{theorem} If $1<a<b$ then the self-referencing sequence beginning with $a$ generated over $\{1, a, b\}$ and the self-referencing sequence beginning with $b$ generated over $\{1, a, b\}$ are independent.
\end{theorem}
\begin{proof}
We proceed by contradiction. If the two sequences are not independent then they must differ by some minimal prefix of length $n$. If we let $a_i$ be the sequence beginning with $a$ and $b_i$ be the sequence beginning with $b$ the
\begin{equation*}
a_{n+k} = b_{k}.
\end{equation*}
We know that the first $b$ terms of the sequence which begins with a $b$ are $b$'s. Because $b>a>1$ no block can be longer then $b$. Thus the terms immediately preceding and following this block in the sequence $a_i$ must not be $b$'s. Because of this the first block of $b_i$ is the $m+1$th block of $a_i$, where $m$ is some positive integer. Since the value of the sequence at position $k$ is also the length of the $k$th block this means that $a_{m+1}=b_1$. In fact the $k$th block of $b_i$ is the $(m+k)$th block of $a_i$ and so 
\begin{equation*}
a_{m+k} = b_k
\end{equation*}

@@

We note that based on a previous step the two sequences differ by a prefix starting at $m$. Since $m<n$ we have produced a prefix which starts before $n$ which is a contradiction. Therefore the two sequences are independent. 
\end{proof}

\section{Equivalence}

\emph{Written by Fermi Ma, edited by Perry Kleinhenz and Erik Waingarten}

The above analysis shows that, for example, the s

\end{document}
